An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-29 draft.tex
biblio added

% Also, multipopulation design of what?x
Multi-population based methods divide the original population into
smaller populations or islands, with every population carrying out the
algorithm independently, with synchronous or asynchronous communication with the
rest of the islands. % exemplify how this is done in different
                     % metaheuristics, especially those we will be
                     % using here - JJ
This relative isolation helps in maintaining an overall
diversity since each population will search in a particular area, at least
between communications. The recombination mentioned above (mixing) or migration
between populations is needed to avoid a premature convergence of candidate
solutions since smaller populations are known to perform better for a given
problem than bigger populations. % Smaller populations converge
                                % prematurely or perform better? - JJ
However, it gives them the added advantage of
parallel operation. Additionally, and in some cases, multi-population algorithms
scale better than expected due to the interaction between the algorithm and the
parallelism of the operation \cite{ALBA20027}. % Need to clarify this
                                % and if it extends to Swarm
                                % algorithms too
                                % Also, is your objective to achieve this superlinear speedup? - JJ

@@

Heterogeneous algorithms add another degree of freedom to the problem of finding
the correct parameter settings for an algorithm; because some parameters affect
the accuracy of the solution and the convergence speed of the algorithms as they
tip the balance between exploration and exploitation of the search space. On the
other hand, current studies show that by having a high number of populations
interacting in parallel, the effect of the individual parameters of each
population is compensated by those selected in other
populations . % reference - JJ

In this work, we will use random settings within a specific range as results have shown
this is a valid solution to this problem. % This should have been
                                % mentioned in the introduction - JJ

@@

Combining multiple algorithms, with different parameters, interacting with each
other at the same time, can benefit from the strengths of each. For instance, a
genetic algorithm could find a promising global solution that is not optimal
while another algorithm, more suitable for a local search, finds the global
optimum. This approach has been followed extensively in recent years with
success. % References - JJ
Moreover, there is a need for frameworks, architecture, and
implementation models that can allow researchers the development of new
parallel, asynchronous, heterogeneous, and parameter-free algorithms in a scalable way.

>>>>

% Also, multipopulation design of what?x
Multi-population based methods divide the original population into
smaller populations or islands, with every population carrying out the
algorithm independently, with synchronous or asynchronous communication with the
rest of the islands \cite{Ma2019}.% exemplify how this is done in different
                     % metaheuristics, especially those we will be
                     % using here - JJ
This relative isolation helps in maintaining an overall
diversity since each population will search in a particular area, at least
between communications. The recombination mentioned above (mixing) or migration
between populations is needed to avoid a premature convergence of candidate
solutions since smaller populations are known to perform better for a given
problem than bigger populations \cite{li2016multi,wu2016differential}. % Smaller populations converge
                                % prematurely or perform better? - JJ
However, it gives them the added advantage of
parallel operation. Additionally, and in some cases, multi-population algorithms
scale better than expected due to the interaction between the algorithm and the
parallelism of the operation \cite{ALBA20027}. % Need to clarify this
                                % and if it extends to Swarm
                                % algorithms too
                                % Also, is your objective to achieve this superlinear speedup? - JJ

@@

Heterogeneous algorithms add another degree of freedom to the problem of finding
the correct parameter settings for an algorithm; because some parameters affect
the accuracy of the solution and the convergence speed of the algorithms as they
tip the balance between exploration and exploitation of the search space. On the
other hand, current studies show that by having a high number of populations
interacting in parallel, the effect of the individual parameters of each
population is compensated by those selected in other
populations \cite{li2016multi,tanabe2013evaluation}. % reference - JJ

In this work, we will use random settings within a specific range as results have shown
this is a valid solution to this problem \cite{garcia2014randomized}. % This should have been
                                % mentioned in the introduction - JJ

@@

Combining multiple algorithms, with different parameters, interacting with each
other at the same time, can benefit from the strengths of each. For instance, a
genetic algorithm could find a promising global solution that is not optimal
while another algorithm, more suitable for a local search, finds the global
optimum. This approach has been followed extensively in recent years with
success \cite{li2015multi,godio2016multi,biswas2014co}. % References - JJ
Moreover, there is a need for frameworks, architecture, and
implementation models that can allow researchers the development of new
parallel, asynchronous, heterogeneous, and parameter-free algorithms in a scalable way.
